---
title: "Readability Test"
author: "Ken Furushima"
date: "8/3/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(tm)
library(pdftools)
library(here)
library(quanteda)
```


# PDF Load
pdf_text
Using the link to google drive is not going to be a good solution to access the file.
It is due to the fact that the google drive link is not the link to the PDF itself but accessing the file through google drive.
In order to access the file, it is necessary to donwload the file locally either as a temp file or permanent file.
When the download file through R, it will be saved as a zip file.

Once the file is saved as pdf file, R can create corpus file directly using quanteda::corpus function.


Reference
https://stackoverflow.com/questions/47851761/r-how-to-read-a-file-from-google-drive-using-r

For those web page readings, we can either extract from the source code (it will be possible but require a bit of coding to deal with each page and might not be ideal if there are multiple sources), or copy the main article into text file.
The latter option can deal with the case when the web page is removed.



```{r}
pdf_text(paste0(here(), "/Data/Wshoes hl.pdf"))

pdftools::pdf_text(paste0(here(), "/Data/Wshoes hl.pdf"))

Corpus(paste0(here(), "/Data/Wshoes hl.pdf"),
       readerControl = list(reader = readPDF))

PDFfile <- paste0(here(), "/Data/Hushed-SJL4 May 2017.pdf")
PDFfile <- paste0(here(), "/Data/Wshoes hl.pdf")
engine <- if(nzchar(system.file(package = "pdftools"))) {
    "pdftools" 
} else {
    "ghostscript"
}
reader <- readPDF(engine)
pdf <- reader(elem = list(uri = PDFfile), language = "en", id = "id1")
cat(content(pdf)[1])
VCorpus(URISource(file, mode = ""),
        readerControl = list(reader = readPDF(engine = "ghostscript")))


pdf_text(PDFfile)

Corpus(PDFfile,
       readerControl = list(reader = readPDF))


tests = c("ARI", "Coleman.Liau.short", "Flesch", "Flesch.Kincaid", "FOG", "Linsear.Write", "SMOG.simple")
tests = c("Flesch", "ARI")
textstat_readability(quanteda::corpus(PDFfile),
                     measure = "Flesch")
textstat_readability(quanteda::corpus(paste0(here(), "/Data/Wshoes hl.pdf")),
                     measure = tests)
textstat_readability(quanteda::corpus(paste0(here(), "/Data/Wshoes hl.txt")),
                     measure = tests)
textstat_readability(quanteda::corpus(paste0(here(), "/Data/Hushed-SJL4 May 2017.txt")),
                     measure = tests)
textstat_readability(quanteda::corpus(paste0(here(), "/Data/Hushed-SJL4 May 2017.pdf")),
                     measure = tests)
textstat_readability(quanteda::corpus(paste0(here(), "/Data/Ako Hiko_Classobs10_Text1_Alvin and Me-SJL3 May 2017.pdf")),
                     measure = tests)
summary(quanteda::corpus(paste0(here(), "/Data/Ako Hiko_Classobs10_Text1_Alvin and Me-SJL3 May 2017.pdf")))
summary(quanteda::corpus(paste0(here(), "/Data/Ako Hiko_Classobs10_Text1_Alvin and Me-SJL3 May 2017.txt")))


quanteda::corpus(paste0(here(), "/Data/test file.txt"))
quanteda::corpus(paste0(here(), "/Data/test file.pdf"))
textstat_readability(quanteda::corpus(paste0(here(), "/Data/test file.txt")),
                     measure = tests)
textstat_readability(quanteda::corpus(paste0(here(), "/Data/test file.pdf")),
                     measure = tests)

test <- pdf_text(paste0(here(), "/Data/test file.pdf"))
length(test)
class(test)
textstat_readability(test,
                     measure = tests)
textstat_readability(pdf_text(paste0(here(), "/Data/Hushed-SJL4 May 2017.pdf")),
                     measure = tests)
textstat_readability(pdf_text(paste0(here(), "/Data/Hushed-SJL4 May 2017 TEST.pdf")),
                     measure = tests)

pdf_text(paste0(here(), "/Data/test file.pdf"))
pdf_text(paste0(here(), "/Data/test file 2.pdf"))
textstat_readability(pdf_text(paste0(here(), "/Data/test file 2.pdf")) %>% readr::read_lines(),
                     measure = tests)
?textstat_readability
```
